% ============================================================
% ABSTRACT
% ============================================================
\newpage
\thispagestyle{plain}

\begin{center}
    {\Large \textbf{Abstract}}\\[1cm]
\end{center}

This thesis details the architectural design and software implementation of an intelligent web platform, specifically engineered for the digital transformation of \textit{Assiette Gala Sfaxienne}. The system addresses complex operational requirements by centralizing and automating core business workflows: culinary catalog administration, transactional order processing, event orchestration, automated quotation issuance, and data-driven governance.

The underlying application infrastructure leverages a microservices-oriented architecture. This paradigm decouples business logic into autonomous entities (authentication, catalog management, orders, events, and artificial intelligence), unified by an API Gateway. Such an architectural pattern ensures high cohesion, loose coupling, and optimal scalability of the overall ecosystem.

To support strategic decision-making, an analytical dashboard, enriched with dynamic graphical components (Recharts), provides management with granular visibility into key performance indicators (KPIs) and sales metrics. Furthermore, the platform integrates advanced business modules covering inventory logistics, supplier relations, digital invoicing, and activity reporting.

The major innovation of this project lies in the integration of a contextual artificial intelligence layer. This is manifested through a conversational agent leveraging the Retrieval-Augmented Generation (RAG) approach, coupled with a FAISS vector database, as well as a predictive recommendation engine. The development lifecycle was rigorously managed using the Scrum agile methodology, structured into five iterations (sprints) to ensure incremental functional validation.

The deliverables of this project demonstrate the technical viability of a sovereign digital ecosystem, perfectly aligned with the constraints of the catering sector, while laying the technical foundations for future evolutions (cloud deployment, advanced analytics, mobile interface).

\vspace{0.8cm}
\noindent\textbf{Keywords:} catering, microservices, artificial intelligence, RAG, FAISS, recommendation system, event management, dashboard, analytics, Scrum.

\clearpage
