% ============================================================
% BIBLIOGRAPHIE
% ============================================================
\renewcommand{\currentchapcolor}{black}
\chapter*{Bibliographie}
\markboth{Bibliographie}{}
\addcontentsline{toc}{chapter}{Bibliographie}

\begin{enumerate}[label={[\arabic*]},series=refs]

    \item E. Gamma, R. Helm, R. Johnson et J. Vlissides, \textit{Design Patterns: Elements of Reusable Object-Oriented Software}, Addison-Wesley, 1994.

    \item S. Newman, \textit{Building Microservices: Designing Fine-Grained Systems}, 2nd Edition, O'Reilly Media, 2021.

    \item C. Richardson, \textit{Microservices Patterns: With Examples in Java}, Manning Publications, 2018.

    \item C. Aubry, \textit{Scrum : Pour une pratique vivante de l'agilité}, 5\textsuperscript{e} édition, Dunod, 2015.

    \item P. Lewis, E. Perez, A. Piktus et al., «\,Retrieval-Augmented Generation for Knowledge-Intensive NLP Tasks\,», \textit{Advances in Neural Information Processing Systems}, vol. 33, pp. 9459--9474, 2020.

    \item A. Vaswani, N. Shazeer, N. Parmar et al., «\,Attention Is All You Need\,», \textit{Advances in Neural Information Processing Systems}, vol. 30, 2017.

    \item Documentation officielle de Node.js : \url{https://nodejs.org/docs/latest/api/}

    \item Documentation officielle de React : \url{https://react.dev/}

    \item Documentation officielle de TypeScript : \url{https://www.typescriptlang.org/docs/}

    \item Documentation officielle Prisma ORM : \url{https://www.prisma.io/docs}

    \item Documentation officielle PostgreSQL : \url{https://www.postgresql.org/docs/}

    \item Documentation officielle Express.js : \url{https://expressjs.com/}

    \item Documentation officielle de LangChain : \url{https://python.langchain.com/docs/}

    \item Documentation officielle de Google Gemini API : \url{https://ai.google.dev/docs}

    \item Documentation Vite : \url{https://vite.dev/guide/}

    \item Documentation Tailwind CSS : \url{https://tailwindcss.com/docs}

    \item Documentation Cloudinary : \url{https://cloudinary.com/documentation}

    \item Documentation FAISS (Facebook AI Similarity Search) : \url{https://github.com/facebookresearch/faiss/wiki}

    \item Documentation officielle de Figma : \url{https://help.figma.com/}

    \item K. Schwaber, J. Sutherland, \textit{The Scrum Guide}, Scrum.org, 2020. Disponible sur : \url{https://scrumguides.org/}

    \item Documentation Recharts : \url{https://recharts.org/en-US/api}

\end{enumerate}

\vspace{1cm}

\chapter*{Webographie}
\markboth{Webographie}{}
\addcontentsline{toc}{chapter}{Webographie}

\begin{enumerate}[label={[\arabic*]},resume=refs]

    \item «\,Microservices Architecture\,», \textit{Microsoft Azure Architecture Center}, consulté le 15/02/2026. \url{https://learn.microsoft.com/en-us/azure/architecture/guide/architecture-styles/microservices}

    \item «\,API Gateway Pattern\,», \textit{Microservices.io}, consulté le 15/02/2026. \url{https://microservices.io/patterns/apigateway.html}

    \item «\,Introduction to RAG\,», \textit{Google Cloud}, consulté le 20/02/2026. \url{https://cloud.google.com/use-cases/retrieval-augmented-generation}

    \item «\,JWT Introduction\,», \textit{jwt.io}, consulté le 10/02/2026. \url{https://jwt.io/introduction}

    \item «\,Sentence Transformers Documentation\,», \textit{HuggingFace}, consulté le 12/03/2026. \url{https://huggingface.co/docs/sentence-transformers/}

    \item «\,Understanding UML Diagrams\,», \textit{Visual Paradigm}, consulté le 05/02/2026. \url{https://www.visual-paradigm.com/guide/uml-unified-modeling-language/}

    \item «\,Scrum Methodology\,», \textit{Atlassian}, consulté le 08/02/2026. \url{https://www.atlassian.com/agile/scrum}

    \item «\,PostgreSQL vs MySQL\,», \textit{DigitalOcean}, consulté le 10/02/2026. \url{https://www.digitalocean.com/community/tutorials/postgresql-vs-mysql}

\end{enumerate}
